Forecasting Gamma-ray Bursts using Gravitational Waves

### 2018-03-19 Paper/Manuscript.tex
Finished a very first draft.

\begin{abstract}
We explore the intriguing possibility of employing future gravitational-wave interferometers to detect the inspiral of compact binaries early enough to alert the electromagnetic observatories so that a gamma-ray burst (GRB) can be observed in its entirety from its very start.
We quantify the ability to predict a GRB by computing the time a canonical binary neutron star (BNS) system takes to inspiral from a certain threshold frequency to its final merger. We define this threshold frequency to be the gravitational-wave frequency at which the RMS-averaged strain due to the BNS system accumulates a signal-to-noise (SNR) ratio of 15. For our computation of advance warning times, we consider BNS systems at luminosity distances of (i) $D\lesssim200\,$Mpc in a three-interferometer network with Advance LIGO's design sensitivity and (ii) $D \lesssim 1000\,$Mpc in a similar network, but with the Einstein Telescope's B configuration
sensitivity. We find in the case of that Advanced LIGO we may get a few minutes of warning time if we get lucky whereas the Einstein Telescope will provide us
with warning times as long as a few hours.
Our main conclusions are: (i) we expect ALV network to forecast 1 to 3 GRBs in the 2020s, (ii)

@@

\section{Introduction}\label{Sec:Intro}
The 6.95\footnote{There have thus far been six detections with $5\sigma$ statistical significance and one additional event, LVT151012 \cite{TheLIGOScientific:2016pea}, with $2\sigma \approx 90\%$ significance hence 6.95 overall.} 
gravitational-wave merger events detected by the Advanced Ligo-Virgo network have firmly established gravitational-wave astronomy
as an observational science \cite{TheLIGOScientific:2016pea, Abbott:2017gyy, Abbott:2017oio, Abbott:2017vtc, GW170817}. 
Though the first event of 14 September 2015 (GW150914 \cite{GW150914}) will always be the ``poster-child'' of this field,
the icing on the cake was the 17 August 2017 (GW170817 \cite{GW170817}) event involving the inspiral and merger of a binary neutron star system with a prompt gamma-ray burst (GRB170817A) detected 1.7 seconds after the coalescence by the Fermi Gamma-ray Burst Monitor \cite{Fermi}{\bf FIX ME} and by the International Gamma-Ray Astrophysics Laboratory {\bf cite}. 
The Advanced-LIGO-Virgo network's initial source localization to within $\sim 31\,\text{degree}^2$ in the Southern skies
enabled astronomers to locate the electromagnetic counterpart in the galaxy NGC 4993 less than 11 hours after the merger, 
first picked up by the One-Meter, Two Hemisphere team {\bf cite}.
This subsequently launched the largest-ever campaign of multi-messenger astronomy across the entire electromagnetic (EM) spectrum still ongoing
more than half a year after the initial GRB \cite{GBM:2017lvd}.

@@

Here, we are interested  in exploring the predictive power of near-future ground-based GW detectors and leave the task of reducing the latency to the experts.
More specifically, we wish to find out how much early warning the GW detectors can provide us before the merger/GRB.
Ref.~\cite{Cannon:2011vi} approached this from an algorithmic perspective by developing computationally inexpensive methods to detect inspiral
signals in GW data to provide early-warning triggers \emph{before} the merger.
We instead focus on the forecasting capabilities of the ground-based interferometers at their \emph{full design} sensitivity by computing the time lag
between the merger and the detection time defined in terms of a certain threshold SNR.
To this end, we consider the $\sim 2020$ ALV network composed of three L-shaped interferometers operating at their design sensitivities
and Einstein Telescope of 2030s.
Ref.~\cite{Nissanke:2012dj} investigated the capabilities of three to five-interferometer detector networks of 2020s in terms of their horizon distance
to inspiralling BNSs and their sky-localization of these sources. Our work here is somewhat complementary in the sense that we are mostly concerned with
advance warning times.

@@

We proceed as follows: Sec.~\ref{sec:BNS_inspiral} introduces the formulation for the leading-order evolution of the binary inspiral.
Sec.~\ref{sec:IFO_response} IFO response

Sec.~\ref{sec:idealizations} idealizations

We reserve the symbol $f$ to denote the GW frequency of the dominant quadrupole mode, which is twice the orbital frequency $f_K$. 
Relatedly, we define the following angular frequencies: $\omega = 2\pi f, \Omega=2\pi f_K$ with $\omega=2\Omega$.
We employ the $\simeq$ symbol for quantities which we can compute exactly, but list finite digits and $\approx$ for quantities whose values we know approximately.
Overdots denote time derivative with respect to detector time, e.g., $\dot{E} =dE/dt$.

@@

\section{GW170817 as a test of our model Advanced LIGO-Virgo network}\label{Sec:GW170817}
On 17 August 2017, at 12:41:04 UTC, GWs from the inspiral and merger of a binary neutron star system were detected by the Advanced LIGO-Virgo network.
The event, first picked up by LIGO Hanford (H1), swept from $\sim 30\,$Hz to $\sim 2000\,$Hz in the detectors' frequency band with an accumulated total SNR of
%18.8, 26.4 and 2.0 at H1, LIGO Livingstone (L1) and Virgo (V1), respectively, yielding 
$\rho_\text{tot} = 32.4$ \cite{GW170817}
The inferred duration of the event in the network bandwidth is $\sim 60\,$ seconds during which $\sim 3000$ cycles of GW were emitted \cite{GW170817_Facts}.
Assuming low-spin priors  ($\chi \le 0.05$, see point 7 of Sec.~\ref{sec:idealizations}), the following values were inferred for the total mass, the chirp mass,
and the luminosity distance of the source with 90\% confidence:
%
\be
M = 2.74^{0.04}_{-0.01} M_\odot, M_c = 1.188^{+0.004}_{-0.002} M_\odot, D= 40^{+8}_{-14}\,\text{Mpc}. \label{eq:GW170817_params}
\ee
%
Note that the error bar for the chirp mass is very small
due to the fact that it can be extracted to high precision over thousands of GW cycles via Eq.~(\ref{eq:fdot}).

@@

Each RMS-averaged strain is accompanied by its shaded region ranging from an optimally oriented strain ($\tilde{H}_h$) to a sub-optimally oriented strain ($\tilde{H}_l$). These regions were first explained in Sec.~\ref{Sec:GW170817} and shown in Fig.~\ref{fig:figGW170817}.

@@

Both Tables~\ref{table:ET} and \ref{table:horizon} clearly show that ET will yield superb SNRs for sources out to 1\,Gpc. Given that
it takes $\gtrsim \mathcal{O}(1)\,$\emph{day} for a BNS source to inspiral from $f_0\sim 1\,$Hz to $\bar{f}$ of Eq.~(\ref{eq:ET_fbar}),
we can expect ET to localize sources within the horizon distance to $\lesssim 1\,\text{deg}^2$ \cite{Mills:2017urp}.
As the ET construction/commissioning timeline is currently uncertain, we can only speculate that ET-C will be operational after 2030 
(this is roughly in line with LISA's timeline).
It is also reasonable to speculate that by that time the detection, localization and early-warning algorithms will have become sufficiently sophisticated
to alert the electromagnetic observatories within an hour of the initial detection (SNR = 15). 
Therefore, we optimistically conclude that 2030s hold in store real-time observations of dozens of gamma ray bursts.
We summarize our major findings for both the ALV network and ET-B/C in Fig.~\ref{fig:summary}.
%
%
%
\begin{table}[h]
\centering
\begin{tabular}{l|ccc}
%toprule
\hline
 & ET-B & & ET-C\T\B\\
\hline
  $D_H $& 87\,Mpc& &{613\,Mpc}\T\\
  $R(D_H) $& $1^{+2}_{-1}\,\text{yr}^{-1}$&\hspace{5mm} &{$355^{+730}_{-280}\,\text{yr}^{-1}$}\T\\
  $\bar\rho_F(D_H)$ & 420 &&{58}\T\B\\
\hline
\end{tabular}
\caption{Horizon distances of ET-B and ET-C assuming $T_\text{AW} =1\,$hour. $R(D_H)$ is the BNS merger rate within a volume of $D_H^3$
obtained by rescaling the rate inferred from GW170817 \cite{GW170817}. $\bar\rho_F(D_H)$ is the total SNR accumulated in ET by a BNS inspiralling at $D_H$ [see Eq.~(\ref{eq:rhoF_ET})].}\label{table:horizon}
\end{table}
%
%
%
\begin{figure}[h!]
\includegraphics[width=\linewidth]{../Figures/Main_results.pdf}
\caption{Summary of our major findings for both the Advanced-LIGO-Virgo (ALV) network circa 2020 and the Einstein Telescope's B and C configurations
ca. 2030. The light coloured (gray) data shows $T_\text{AW}$ for the ALV network (dotted), ET-B (dashed), and ET-C (solid), respectively.
The connecting light (gray) lines are drawn only for visualization purposes unlike the dark (brown) lines coming from the $D^{-2}$ powerlaw in the SNR [see Eq.~(\ref{eq:ET_SNRsq}] which is plotted on the right axis. 
We used $D=50,100,200\,$Mpc to obtain the ALV results (Sec.~\ref{Sec:ALIGO2020}) and $D\ge 100\,$Mpc for the ET results.}\label{fig:summary}
\end{figure}

@@

\section{Binary black hole neutron star systems}
In this section, we investigate the possibility of witnessing the tidal distruption of a neutron star by a black hole before the merger.
The treatment of the inspiral is the same as before, however the fate of the neutron star depends strongly on the system's intrinsic parameters
such as the black hole mass and spin, and the neutron star's equation of state (EOS) and compactness $c_\text{NS}\equiv G M_\text{NS}/(R_\text{NS}c^2)$. 
The evolution of black hole-neutron star (BH-NS) binaries is a very active field of research at the interface of numerical relativity and high-energy astrophysics
(see Ref. \cite{Shibata:2011jka} for a comprehensive review) requiring fully general relativistic magnetohydrodynamic treatment including neutrino transport equations.
The complexity of evolving the dynamics of these systems require large computational resources and long runtimes.
%running on large-scale clusters.
As such, the details are beyond the scope of this article, but we can use a mostly Newtonian treatment to serve our purposes. %, however the numerical simulationshave verified

@@

$c_R >1 $. Setting $m_2= M_\text{BH}, m_1 = M_\text{NS}$, and $r_1=r_\text{NS}$, we can roughly take the above condition to be

@@

\f{m_2}{m_1} \gtrsim \left(\f{r}{r_1}\right)^3 \label{eq:TD_cond2}.

@@

100 &   28.2\,minutes & 503 &{\qquad} &  2.15\,hours & 601\T\\
200 & 8.21\,minutes & 251  &{\qquad} & 1.10\,hours & 300 \\
400 &  2.00\,minutes & 124 &{\qquad} & 34.2\,minutes & 148\\
1000 & 14.3\,seconds & 49 &{\qquad} & 13.9\,minutes& 58.5\\
\hline
%bottomrule
\end{tabular}
\caption{Same as Table~\ref{table:ET}, but now for a $5 M_\odot- 1.4 M_\odot$ black hole-neutron star binary.
The SNR is even higher than before, however the advance warning times have decreased significantly.}\label{table:ET_BH_NS}
\end{table}
%
%
\\
\noindent
From the table, we can see that the horizon distance of ET-C for these binaries with $T_\text{AW} \approx 1\,$hour is roughly 200\,Mpc.
Given that the LIGO O1 merger rate for these systems is $ R < 3600\,$Gpc$^{-3}$yr$^{-1}$ \cite{Abbott:2016ymx},
there could be 28.8 such mergers per year within ET-C's horizon distance. We must emphasize that this should be viewed
as an upper limit as low-mass, high-spin black holes such as ours above are expected to be rare.
Therefore, we realistically expect ET-C to forecast $\sim \mathcal{O}(1)$ tidal disruption event per year.
A better estimation would need to incorporate the percentage of such black holes from population studies and Monte-Carlo simulations,
however, all of these come with rather large error bars {\bf CITE}.
%and that no TD occurs for $a=0$. This is roughly consistent with Fig.5 of Ref.~\cite{Hanna:2008um}
%Choosing lower mass implies reduced SNR since $\rho \propto M_c^{5/3} \propto (1+Q)^{1/3}/Q$,
%but even with $m_2=5 M_\odot$, a BH-NS binary is ``louder'' than a BNS system at the same distance. 
%and as we showed in Sec.~\ref{sec:results}, low SNR is not going to be a problem with ET sensitivities out to $D \sim 1\,$Gpc.
%
%It is straightforward to show that this mass bound is only consistent with spinning black holes by substituting the naive Schwarzschild $r_\text{ISCO}$ value 
%into Eq~.(\ref{eq:TD_cond1}) along with $c_R=1.7$ {\bf CITE} which yield $M_\text{BH} \lesssim 4.1 M_\odot$ violating the above BH mass bound.
%ISCO location from NR 
%\be
%\Omega_\text{ISCO} M = 0.068 \left[ 1- \f{0.444}{Q^{1/4}}(1-3.54 C^{1/3})\right] 
%\ee

>>>>

\begin{abstract}
We explore the intriguing possibility of employing future ground-based gravitational-wave interferometers to detect the inspiral of binary neutron stars early enough to alert the electromagnetic observatories so that a gamma-ray burst (GRB) can be observed in its entirety from its very start.
We quantify the ability to predict a GRB by computing the time a binary neutron star (BNS) system takes to inspiral from a its moment of detection to its final merger. We define the moment of detection to be given when the inteferometer network accumulates a signal-to-noise ratio of 15. %for the BNS inspiral.
For our computations, %of advance warning times, 
we specifically consider BNS systems at luminosity distances of (i) $D\le200\,$Mpc in the three-interferometer Advanced-LIGO-Virgo network of 2020, and (ii) $D \le 1000\,$Mpc in the Einstein Telescope's B and C configurations. 
In the case of Advanced LIGO-Virgo we find that we may at best get a few minutes of warning time thus we expect no forecast of GRBs in the 2020s. 
On the other hand, we demonstrate that Einstein Telescope will provide us with warning times as long as a few hours, more specifically, greater than an hour
for BNS inspirals closer than roughly 600\,Mpc. Taking this luminosity distance to be our horizon distance, 
we show that we expect to forecast $\gtrsim \ord(10^2)$ GRBs in the 2030s using the C configuration of Einstein Telescope.
We reapply our computation to binary black hole - neutron star inspirals and find that we expect 1 to 3 tidal disruption events 
to be forecast by the same detector.
%Our main conclusions are: (i) we expect ALV network to forecast 1 to 3 GRBs in the 2020s, (ii)

@@

\section{Introduction}\label{Sec:Intro}
The 6.95\footnote{There have thus far been six detections with $5\sigma$ statistical significance and one additional event, LVT151012 \cite{TheLIGOScientific:2016pea}, with $2\sigma \simeq 95\%$ significance hence 6.95 overall.} 
gravitational-wave merger events detected by the Advanced Ligo-Virgo network have firmly established gravitational-wave astronomy
as an observational science \cite{TheLIGOScientific:2016pea, Abbott:2017gyy, Abbott:2017oio, Abbott:2017vtc, GW170817}. 
Though the first event of 14 September 2015 (GW150914 \cite{GW150914}) will always be the ``poster-child'' of this field,
the icing on the cake was the 17 August 2017 (GW170817 \cite{GW170817}) event involving the inspiral and merger of a binary neutron star system with a prompt gamma-ray burst (GRB170817A) detected 1.7 seconds after the coalescence by the Fermi Gamma-ray Burst Monitor \cite{Fermi}{\bf FIX ME} and by the International Gamma-Ray Astrophysics Laboratory {\bf cite}. 
The Advanced-LIGO-Virgo network's initial source localization to within $\sim 31\,\text{degree}^2$ in the Southern skies
enabled astronomers to locate the electromagnetic counterpart in the galaxy NGC 4993 less than 11 hours after the merger, 
first picked up by the One-Meter, Two Hemisphere team {\bf cite}.
This subsequently launched the largest-ever campaign of multi-messenger astronomy across the entire electromagnetic (EM) spectrum still ongoing
more than half a year after the initial GRB \cite{GBM:2017lvd}.

@@

Here, we are interested  in exploring the predictive power of near-future ground-based GW detectors thus leave the task of reducing the latency to the experts.
More specifically, we wish to find out how much early warning the GW detectors can provide us before the merger/GRB.
Ref.~\cite{Cannon:2011vi} approached this from an algorithmic perspective by developing computationally inexpensive methods to detect inspiral
signals in GW data to provide early-warning triggers \emph{before} the merger.
We instead focus on the forecasting capabilities of the ground-based interferometers at their \emph{full design} sensitivity by computing the time lag
between the merger and the detection time defined in terms of a certain threshold SNR.
To this end, we consider the $\sim 2020$ ALV network composed of three L-shaped interferometers operating at their design sensitivities
and Einstein Telescope of 2030s.
Ref.~\cite{Nissanke:2012dj} investigated the capabilities of three to five-interferometer detector networks of 2020s in terms of their horizon distance
to inspiralling BNSs and their sky-localization of these sources. Our work here is somewhat complementary in the sense that we are mostly concerned with
advance warning times.

@@

This article is organized as follows. Sec.~\ref{sec:BNS_inspiral} introduces the formulation for the leading-order evolution of the binary inspiral.
Sec.~\ref{sec:IFO_response} details the interferometer response to GWs based on topology.
Sec.~\ref{sec:idealizations} lists the various idealizations we employ to simplify our treatment and supplies justification for each.
Sec.~\ref{sec:GW170817} tests our model network and evolution using the parameters of GW170817 and the corresponding GW data.
Sec.~\ref{sec:results} contains our main results presented as advance warning times in Tables~\ref{table:LIGO2020}, \ref{table:ET} 
as well horizon distances and event rates in Table~\ref{table:horizon}.
In Sec.~\ref{sec:BH_NS}, we reapply the above procedure to black hole - neutron star inspirals to see whether or not 
future detectors can forecast a tidal disruption event, for which we summarize our findings in Table~\ref{table:ET_BH_NS}.

We reserve the symbol $f$ to denote the GW frequency of the dominant quadrupole mode, which is twice the orbital (Keplerian) frequency $f_K$. 
Relatedly, we define the following angular frequencies: $\omega = 2\pi f, \Omega=2\pi f_K$ with $\omega=2\Omega$.
We employ the $\simeq$ symbol for the numerical values of quantities with infinite decimal expansions which we usually truncate at four significant digits,
e.g., $\pi \simeq 3.142$.
The $\approx$ symbol is reserved for approximations, whereas $\sim$ denotes rather rough order-of-magnitude equalities, e.g., $\pi \sim \ord(1)$. %Kepler's third law: $f_K^2\sim r^{-3}$.
Overdots denote time derivative with respect to detector-frame time, e.g., $\dot{E} =dE/dt$. Unless otherwise noted, we use standard SI units.

@@

\section{GW170817 as a test of our model Advanced LIGO-Virgo network}\label{sec:GW170817}
On 17 August 2017, at 12:41:04 UTC, GWs from the inspiral and merger of a binary neutron star system were detected by the Advanced LIGO-Virgo network.
The event, first picked up by LIGO Hanford (H1), swept from $\sim 30\,$Hz to $\sim 2000\,$Hz in the detectors' frequency band with an accumulated total SNR of
%18.8, 26.4 and 2.0 at H1, LIGO Livingstone (L1) and Virgo (V1), respectively, yielding 
$\rho_\text{tot} = 32.4$ \cite{GW170817}
The inferred duration of the event in the network bandwidth is $\sim 60\,$ seconds during which $\sim 3000$ cycles of GW were emitted \cite{GW170817_Facts}.
Assuming low-spin priors  ($\chi \le 0.05$, see point 7 of Sec.~\ref{sec:idealizations}), the following values were inferred for the total mass, the chirp mass,
and the luminosity distance of the source with 90\% confidence:
%
\be
M = 2.74^{0.04}_{-0.01} M_\odot, M_c = 1.188^{+0.004}_{-0.002} M_\odot, D= 40^{+8}_{-14}\,\text{Mpc}. \label{eq:GW170817_params}
\ee
%
Note that the error bar for the chirp mass is very small
due to the fact that it can be extracted to high precision over thousands of GW cycles via Eq.~(\ref{eq:fdot}).

@@

Each RMS-averaged strain is accompanied by its shaded region ranging from an optimally oriented strain ($\tilde{H}_h$) to a sub-optimally oriented strain ($\tilde{H}_l$). These regions were first explained in Sec.~\ref{sec:GW170817} and shown in Fig.~\ref{fig:figGW170817}.

@@

Both Tables~\ref{table:ET} and \ref{table:horizon} clearly show that ET will yield superb SNRs for sources out to 1\,Gpc. Given that
it takes $\gtrsim \mathcal{O}(1)\,$\emph{day} for a BNS source to inspiral from $f_0\sim 1\,$Hz to $\bar{f}$ of Eq.~(\ref{eq:ET_fbar}),
we can expect ET to localize sources within the horizon distance to $\lesssim 1\,\text{deg}^2$ \cite{Mills:2017urp}.
As the ET construction/commissioning timeline is currently uncertain, we can only speculate that ET-C will be operational after 2030 
(this is roughly in line with the milli-Hertz space interferometer LISA's timeline \cite{Audley:2017drz}).
It is also reasonable to speculate that by that time the detection, localization and early-warning algorithms will have become sufficiently sophisticated
to alert the electromagnetic observatories within an hour of the initial detection (SNR = 15). 
Therefore, we optimistically conclude that 2030s hold in store real-time observations of dozens of gamma ray bursts.
We summarize our major findings for both the ALV network and ET-B/C in Fig.~\ref{fig:summary}.
%
%
%
\begin{table}[h]
\centering
\begin{tabular}{l|ccc}
%toprule
\hline
 & ET-B & & ET-C\T\B\\
\hline
  $D_H $& 87\,Mpc& &{613\,Mpc}\T\\
  $R(D_H) $& $1^{+2}_{-1}\,\text{yr}^{-1}$&\hspace{5mm} &{$355^{+730}_{-280}\,\text{yr}^{-1}$}\T\\
  $\bar\rho_F(D_H)$ & 420 &&{58}\T\B\\
\hline
\end{tabular}
\caption{Horizon distances of ET-B and ET-C assuming $T_\text{AW} =1\,$hour. $R(D_H)$ is the BNS merger rate within a volume of $D_H^3$
obtained by rescaling the rate inferred from GW170817 \cite{GW170817}. $\bar\rho_F(D_H)$ is the total SNR accumulated in ET by a BNS inspiralling at $D_H$ [see Eq.~(\ref{eq:rhoF_ET})].}\label{table:horizon}
\end{table}
%
%
%
\begin{figure}[h!]
\includegraphics[width=\linewidth]{../Figures/Main_results.pdf}
\caption{Summary of our major findings for both the Advanced-LIGO-Virgo (ALV) network circa 2020 and the Einstein Telescope's B and C configurations
ca. 2030. The light coloured (gray) data shows $T_\text{AW}$ for the ALV network (dotted), ET-B (dashed), and ET-C (solid), respectively.
The connecting light (gray) lines are drawn only for visualization purposes unlike the dark (brown) lines coming from the $D^{-2}$ powerlaw in the SNR [see Eq.~(\ref{eq:ET_SNRsq}] which is plotted on the right axis. 
We used $D=50,100,200\,$Mpc to obtain the ALV results (Sec.~\ref{Sec:ALIGO2020}) and $D\ge 100\,$Mpc for the ET results.}\label{fig:summary}
\end{figure}

@@

\section{Binary black hole neutron star systems}\label{sec:BH_NS}
In this section, we investigate the possibility of witnessing the tidal distruption of a neutron star by a black hole before the merger.
The treatment of the inspiral is the same as before, however the fate of the neutron star depends strongly on the system's intrinsic parameters
such as the black hole mass and spin, and the neutron star's equation of state (EOS) and compactness $c_\text{NS}\equiv G M_\text{NS}/(R_\text{NS}c^2)$. 
The evolution of black hole-neutron star (BH-NS) binaries is a very active field of research at the interface of numerical relativity and high-energy astrophysics
(see Ref. \cite{Shibata:2011jka} for a comprehensive review) requiring fully general relativistic magnetohydrodynamic treatment including neutrino transport equations.
The complexity of evolving the dynamics of these systems require large computational resources and long runtimes.
%running on large-scale clusters.
As such, the details are beyond the scope of this article, but we can use a mostly Newtonian treatment to serve our purposes. %, however the numerical simulationshave verified

@@

$c_R >1 $. %Setting $m_2= M_\text{BH}, m_1 = M_\text{NS}$, and $r_1=r_\text{NS}$, 
We can roughly take the above condition to be

@@

\f{M_\text{BH}}{M_\text{NS}} \gtrsim \left(\f{r}{R_\text{NS}}\right)^3 \label{eq:TD_cond2}.

@@

100 &   28.2\,minutes & 503 &{\qquad} &  2.15\,hours & 601\T\\
200 & 8.21\,minutes & 251  &{\qquad} & 1.10\,hours & 300 \\
400 &  2.00\,minutes & 124 &{\qquad} & 34.2\,minutes & 148\\
1000 & 14.3\,seconds & 49 &{\qquad} & 13.9\,minutes& 58.5\\
\hline
%bottomrule
\end{tabular}
\caption{Same as Table~\ref{table:ET}, but now for a $5 M_\odot- 1.4 M_\odot$ black hole-neutron star binary.
The SNR is even higher than before, however the advance warning times have decreased significantly.}\label{table:ET_BH_NS}
\end{table}
%
%
\\
\noindent
From the table, we can see that the horizon distance of ET-C for these binaries with $T_\text{AW} \approx 1\,$hour is roughly 200\,Mpc.
Given that the LIGO O1 merger rate for these systems is $ R < 3600\,$Gpc$^{-3}$yr$^{-1}$ \cite{Abbott:2016ymx},
there could be 28.8 such mergers per year within ET-C's horizon distance of $\approx 200\,$Mpc corresponding roughly to $T_\text{AW}\approx1\,$hour.
We must emphasize that this should be viewed
as an upper limit as low-mass, high-spin black holes such as ours above are expected to be rare.
Theoretical studies indicate that $\lesssim 10\%$ stellar-mass BHs have masses $\lesssim 5 M_\odot$ \cite{Fryer:1999ht}.
This seems to be supported at least by observations of galactic black holes \cite{Ozel:2010su}.
Therefore, we realistically expect ET-C to forecast $\lesssim 3$ tidal disruption events per year.
%A better estimation would need to incorporate the percentage of such black holes from population studies and Monte-Carlo simulations,
%however, all of these come with rather large error bars.
%and that no TD occurs for $a=0$. This is roughly consistent with Fig.5 of Ref.~\cite{Hanna:2008um}
%Choosing lower mass implies reduced SNR since $\rho \propto M_c^{5/3} \propto (1+Q)^{1/3}/Q$,
%but even with $m_2=5 M_\odot$, a BH-NS binary is ``louder'' than a BNS system at the same distance. 
%and as we showed in Sec.~\ref{sec:results}, low SNR is not going to be a problem with ET sensitivities out to $D \sim 1\,$Gpc.
%
%It is straightforward to show that this mass bound is only consistent with spinning black holes by substituting the naive Schwarzschild $r_\text{ISCO}$ value 
%into Eq~.(\ref{eq:TD_cond1}) along with $c_R=1.7$ {\bf CITE} which yield $M_\text{BH} \lesssim 4.1 M_\odot$ violating the above BH mass bound.
%ISCO location from NR 
%\be
%\Omega_\text{ISCO} M = 0.068 \left[ 1- \f{0.444}{Q^{1/4}}(1-3.54 C^{1/3})\right] 
%\ee
\section{Outlook}
By constructing representative models of the near-future ground-based gravitational-wave interferometers, we investigated the possibility of
forecasting gamma-ray burts resulting from the merger of two neutron stars.
We showed that we do not expect the Advanced-LIGO-Virgo network to provide such a forecast in the 2020s unless we get extremely lucky
and detect a BNS inspiral in our galaxy which is roughly a one-in-a-trillion shot (in years). %($\sim 1$ per trillion years lucky).
However, the odds completely change in our favour with Einstein Telescope's B and especially C configurations, 
the latter of which is expected to forecast $\gtrsim \ord(10^2)$ GRBs per year as we show in Table~\ref{table:horizon}. 
The same configuration should also forecast up to three tidal disruption events per year in which a high-spin, low-stellar-mass
black hole tidally tears apart its companion neutron star.
The beginning of operation for the C configuration will roughly coincide with the launch of the LISA mission.
Additionally, there are proposals to launch another space interferometer called DECIGO which will operate
between $0.1$ and 10 Hz thus bridging the gap between LISA and the ground-based interferometers \cite{Sato:2009zzb, Kawamura:2006zz}.
With the gravitational-wave sky virtually covered from $10^{-4}$ to $10^3\,$Hz, we will suffer from the 
embarassment of the riches in the 2030s. In short, the future of gravitational and multi-messenger astronomy is bright.

\acknowledgements 
SA thanks Conor O'Toole for endless feedback and Niels Warburton for a careful reading of this article.
